A simplified dynamic bioenergetic model for coral-*Symbiodinium* symbioses and coral bleaching as an alternate stable state

### 2016-11-23 JTB_supp/JTB_supp.Rmd
update title
Change dt to 0.1 in Fig S9

---
title: "A simplified dynamic bioenergetic model for coral-algal symbiosis and coral bleaching"
author: "Ross Cunning, Erik B. Muller, Ruth D. Gates, Roger M. Nisbet"
output: html_document
bibliography: library.bib
---

@@

# Figure S9. Overshoot of symbiont density following bleaching.
```{r FigS9, cache=T}
# Set run time vector
time <- seq(-100, 1095, 0.5)  # if single model run, use time input

>>>>

---
title: A simplified dynamic bioenergetic model for coral-*Symbiodinium* symbioses and coral bleaching as an alternate stable state
author: "Ross Cunning, Erik B. Muller, Ruth D. Gates, Roger M. Nisbet"
output: html_document
bibliography: library.bib
---

@@

# Figure S9. Overshoot of symbiont density following bleaching.
```{r FigS9, cache=T}
# Set run time vector
time <- seq(-100, 1095, 0.1)  # if single model run, use time input
